%-------------------------
% Modern Resume in LaTeX
% Author : Kunal Yelne  
% Updated with business impact focus
%------------------------

\documentclass[letterpaper,11pt]{article}

% Modern font packages - choose one of these options
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

% FONT OPTIONS - Uncomment one of these for different looks:

% Option 1: Source Sans Pro (Modern, clean sans-serif)
% \usepackage[default]{sourcesanspro}

% Option 2: Fira Sans (Clean, technical look)
% \usepackage[sfdefault]{FiraSans}

% Option 3: Roboto (Google's font, very modern)
% \usepackage[sfdefault]{roboto}

% Option 4: Lato (Professional, readable)
% \usepackage[default]{lato}

% Option 5: Open Sans (Popular web font)
% \usepackage[default]{opensans}

% For math and symbols compatibility
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\input{glyphtounicode}

% Define modern colors
\definecolor{primarycolor}{RGB}{0, 0, 0}        % Pure black for headings and name
\definecolor{accentcolor}{RGB}{64, 64, 64}      % Rich dark gray for accents
\definecolor{textcolor}{RGB}{32, 32, 32}        % Dark charcoal for body text

% FontAwesome icons with proper parameter handling
\usepackage{ifthen}
\usepackage{textcomp}
\IfFileExists{fontawesome5.sty}{%
  \usepackage{fontawesome5}
  \newcommand{\mobileicon}{{\color{primarycolor}\faMobile}}
  \newcommand{\emailicon}{{\color{primarycolor}\faEnvelope}}
  \newcommand{\githubicon}{{\color{primarycolor}\faGithub}}
  \newcommand{\linkedinicon}{{\color{primarycolor}\faLinkedin}}
}{%
  % Fallback to marvosym package for basic icons
  \usepackage{marvosym}
  \newcommand{\mobileicon}{{\color{primarycolor}\Mobilefone}}
  \newcommand{\emailicon}{{\color{primarycolor}\Letter}}
  \newcommand{\githubicon}{{\color{primarycolor}\ComputerMouse}}
  \newcommand{\linkedinicon}{{\color{primarycolor}\Info}}
}

% Simple contact commands without parameter conflicts
\newcommand{\mobile}[1]{\mobileicon\ #1} 
\newcommand{\email}[1]{\emailicon\ \href{mailto:#1}{\color{primarycolor}#1}} 
\newcommand{\github}[1]{\githubicon\ \href{https://github.com/#1}{\color{primarycolor}#1}} 
\newcommand{\linkedin}[1]{\linkedinicon\ \href{https://www.linkedin.com/in/#1}{\color{primarycolor}#1}}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins for modern look
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.2in}

% Fix footer spacing
\setlength{\footskip}{4.08003pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Modern sections formatting
\titleformat{\section}{
  \vspace{-8pt}\color{primarycolor}\bfseries\large\raggedright
}{}{0em}{}[\color{primarycolor}\titlerule \vspace{-6pt}]

% Ensure PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands with modern styling
\newcommand{\resumeItem}[1]{
  \item\small\color{textcolor}{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\color{primarycolor}#1} & \color{accentcolor}\textbf{#2} \\
      \textit{\color{textcolor}\small#3} & \textit{\color{accentcolor}\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\color{textcolor}\small#1} & \textit{\color{accentcolor}\small #2} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \small\color{textcolor}#1 & \color{accentcolor}#2 \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-3pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge\bfseries\color{primarycolor} KUNAL YELNE} \\[4pt]
    {\large\color{accentcolor} Senior Software Engineer | Mobile \& Backend Systems} \\[8pt]
    
    \mobile{(+91) 7038499489} \hspace{8pt}$\bullet$\hspace{8pt} 
    \email{kunal.s.yelne@gmail.com} \hspace{8pt}$\bullet$\hspace{8pt}
    \linkedin{kunalyelne} \hspace{8pt}$\bullet$\hspace{8pt}
    \github{kunalyelne}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\begin{itemize}[leftmargin=0.15in, label={}]
   \small{\item\color{textcolor}{
    Senior Software Engineer with \textbf{6+ years} building scalable mobile and backend systems using \textbf{Swift, Kotlin, Go, and cloud technologies}. Led initiatives serving \textbf{1M+ managed devices}, improved deployment pipelines by \textbf{over 90\%}, and increased test coverage from 40\% to 95\%. Experience mentoring junior engineers and collaborating across cross-functional teams in fast-paced environments.
   }}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Esper}{Bengaluru, IN}
      {Senior Software Engineer}{September 2021 -- December 2025}
      \resumeItemListStart
        \resumeItem{Architected industry-first DevOps feature \textbf{"Blueprints"} that reduced compliance management time by \textbf{80\%} for enterprise customers managing dedicated device fleets at scale.}
        \resumeItem{Engineered Device Policy Controller handling \textbf{1M+ Android devices} across 50+ OEMs, achieving \textbf{99.9\% uptime} and reducing device provisioning failures by \textbf{65\%}.}
        \resumeItem{Delivered cross-platform MDM solution supporting iOS devices, expanding market reach by \textbf{30\%} and enabling enterprise customers to manage mixed device ecosystems seamlessly.}
        \resumeItem{Led quality improvement initiative increasing unit test coverage from \textbf{40\% to 95\%} and implementing comprehensive integration testing, resulting in \textbf{70\% reduction} in production incidents and improved system reliability.}
        \resumeItem{Eliminated deployment-related incidents by implementing systematic testing protocols, saving \textbf{15+ hours/week} in debugging and significantly improving customer satisfaction scores.}
        \resumeItem{Streamlined cross-functional collaboration processes, reducing feature delivery time by \textbf{25\%} through improved communication between engineering, QA, product, and support teams.}
      \resumeItemListEnd

    \resumeSubheading
      {Butter Chicken Studios}{Remote}
      {Founder \& Lead Engineer}{2025 -- Present}
      \resumeItemListStart
        \resumeItem{Built end-to-end fitness platform \textbf{Fitlane} from concept to production, designing scalable architecture that supports future growth to \textbf{100K+ users} with minimal infrastructure overhead.}
        \resumeItem{Reduced infrastructure provisioning time from \textbf{weeks to hours} through Infrastructure as Code implementation, enabling rapid feature deployment and A/B testing capabilities.}
        \resumeItem{Implemented containerized CI/CD pipelines reducing deployment time \textbf{from 2 hours to 5 minutes}, enabling rapid iteration cycles and improved developer productivity.}
        \resumeItem{Implemented auto-scaling infrastructure that automatically handles traffic spikes up to \textbf{10x normal load}, ensuring zero downtime during peak usage periods.}
        \resumeItem{Integrated AI-powered personalization engine that increased user engagement by \textbf{35\%} through customized fitness recommendations and automated content generation.}
      \resumeItemListEnd

    \resumeSubheading
      {Vyapar}{Bengaluru, IN}
      {Software Development Engineer}{July 2021 -- September 2021}
      \resumeItemListStart
        \resumeItem{Enhanced business accounting platform serving \textbf{10M+ Indian SMEs}, optimizing invoice processing workflows that reduced manual data entry time by \textbf{60\%} for small business owners.}
        \resumeItem{Implemented advanced business analytics dashboard that helped \textbf{500K+ businesses} make data-driven decisions, resulting in improved cash flow management and inventory optimization.}
      \resumeItemListEnd

    \resumeSubheading
      {Collegedunia Web Private Limited}{Gurugram, IN}
      {Android Developer}{July 2020 -- July 2021}
      \resumeItemListStart
        \resumeItem{Engineered reusable news feature library that reduced development time by \textbf{40\%} across multiple apps, leading to faster feature delivery and consistent user experience for \textbf{5M+ users}.}
        \resumeItem{Redesigned ticket management system and UI/UX that improved user satisfaction scores by \textbf{50\%} and reduced support response time by \textbf{35\%}, directly impacting customer retention.}
        \resumeItem{Optimized app performance reducing crash rates by \textbf{60\%} and improving app store ratings from 3.2 to 4.1 stars, resulting in \textbf{25\% increase} in organic downloads.}
      \resumeItemListEnd

    \resumeSubheading
      {NPCIL, DAE, Govt. of India}{Mumbai, IN}
      {Software Development Intern}{May 2019 -- Dec. 2019}
      \resumeItemListStart
        \resumeItem{Automated data synchronization between critical systems, eliminating \textbf{15+ hours/week} of manual data entry and reducing human errors in nuclear plant operations by \textbf{90\%}.}
        \resumeItem{Developed real-time safety monitoring interface that improved reactor status visibility for operators, contributing to enhanced safety protocols and faster emergency response times.}
        \resumeItem{Created intuitive drag-and-drop visualization tool that reduced operator training time by \textbf{30\%} while maintaining strict nuclear industry safety and reliability standards.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Information Technology Nagpur}{Nagpur, IN}
      {B.Tech In Computer Science and Engineering, CGPA: 8.08}{July 2016 -- July 2020}
  \resumeSubHeadingListEnd

%-----------CORE EXPERTISE-----------
\section{Core Technical Expertise}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item\color{textcolor}{
     \textbf{\color{primarycolor}Mobile Application Architecture}{: Expertise in iOS/Android development using modern frameworks (SwiftUI, Jetpack Compose), MVVM patterns, and cross-platform solutions} \\[2pt]
     \textbf{\color{primarycolor}Backend Systems \& APIs}{: Proficient in designing scalable microservices, RESTful APIs, database optimization, and distributed system patterns} \\[2pt]
     \textbf{\color{primarycolor}Cloud Infrastructure \& DevOps}{: Hands-on experience with AWS/GCP services, containerization, Infrastructure as Code, and CI/CD pipeline automation} \\[2pt]
     \textbf{\color{primarycolor}Quality Engineering}{: Strong advocate for test-driven development, automated testing strategies, code review processes, and production monitoring} \\[2pt]
     \textbf{\color{primarycolor}Technical Leadership}{: Experience mentoring junior developers, driving technical decisions, and collaborating across cross-functional teams in agile environments}
    }}
 \end{itemize}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item\color{textcolor}{
     \textbf{\color{primarycolor}Languages}{: Go, Swift, Kotlin, Java, Python, JavaScript/TypeScript, C++} \\[2pt]
     \textbf{\color{primarycolor}Mobile Development}{: iOS (SwiftUI, UIKit, Combine), Android (Jetpack Compose, Architecture Components), React Native} \\[2pt]
     \textbf{\color{primarycolor}Backend \& Databases}{: Node.js, PostgreSQL, Redis, RESTful APIs, GraphQL, Microservices Architecture} \\[2pt]
     \textbf{\color{primarycolor}Cloud \& Infrastructure}{: AWS (Lambda, RDS, S3, ECS), GCP, Docker, Kubernetes, Terraform, CI/CD Pipelines} \\[2pt]
     \textbf{\color{primarycolor}Tools \& Practices}{: Git, GitHub Actions, Infrastructure as Code, Test-Driven Development, Agile/Scrum}
    }}
 \end{itemize}

%-----------KEY PROJECTS-----------
\section{Selected Project Highlights}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item\color{textcolor}{
     \textbf{\color{primarycolor}Enterprise MDM Platform}: Co-architected device management system handling \textbf{1M+ Android/iOS devices} across multiple OEMs. Contributed to features that reduced customer onboarding time and improved enterprise adoption. \\[3pt]
     \textbf{\color{primarycolor}Fitlane Fitness Platform}: End-to-end development of mobile app and backend services using modern architecture (SwiftUI, Go microservices, PostgreSQL). Implemented Infrastructure as Code and automated deployment pipelines. \\[3pt]
     \textbf{\color{primarycolor}Quality Engineering Initiative}: Led testing strategy improvements across multiple codebases, establishing automated testing frameworks and monitoring systems that significantly reduced production issues.
    }}
 \end{itemize}

 %-----------RECOGNITION-----------
\section{Professional Recognition}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item\color{textcolor}{
     {Selected for \textbf{\color{primarycolor}ACM ICPC} Amritapuri Regional 2018, demonstrating competitive programming excellence and algorithmic problem-solving capabilities.} \\[2pt]
     {Won \textbf{\color{primarycolor}1st place} at Esper Spark Hackathon for innovative Mobile Device Management solution that directly contributed to product roadmap and customer value delivery.}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
